Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-29 reports/manuscript/paper.tex
Add required acknowledgements to data providers.

This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
National Institutes for Mental Health, by a grant from the Gordon \& Betty
Moore Foundation and the Alfred P. Sloan Foundation to the University of
Washington eScience Institute Data Science Environment, and by the Google
Cloud Platform Academic Research Credits Program. We would like to thank
Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
and John Kruper
for helpful comments on the manuscript.

>>>>

This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
National Institutes for Mental Health, by a grant from the Gordon \& Betty
Moore Foundation and the Alfred P. Sloan Foundation to the University of
Washington eScience Institute Data Science Environment, and by the Google
Cloud Platform Academic Research Credits Program. We would like to thank
Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
and John Kruper
for helpful comments on the manuscript. Data collection and sharing for this project was provided by the Cambridge Centre for Ageing and Neuroscience (CamCAN). CamCAN funding was provided by the UK Biotechnology and Biological Sciences Research Council (grant number BB/H008217/1), together with support from the UK Medical Research Council and University of Cambridge, UK. This manuscript was prepared using a limited access dataset obtained from the Child Mind Institute Biobank, The Healthy Brain Network dataset. This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute

### 2021-04-29 reports/manuscript/paper_changes.tex
Add required acknowledgements to data providers.

This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
National Institutes for Mental Health, by a grant from the Gordon \& Betty
Moore Foundation and the Alfred P. Sloan Foundation to the University of
Washington eScience Institute Data Science Environment, and by the Google
Cloud Platform Academic Research Credits Program. We would like to thank
Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
\added{and John Kruper}
for helpful comments on the manuscript.

>>>>

This work was supported by BRAIN Iniative grant 1RF1MH121868-01 from the
National Institutes for Mental Health, by a grant from the Gordon \& Betty
Moore Foundation and the Alfred P. Sloan Foundation to the University of
Washington eScience Institute Data Science Environment, and by the Google
Cloud Platform Academic Research Credits Program. We would like to thank
Scott Murray for a useful discussion of the SGL method and Mareike Grotheer
\added{and John Kruper}
for helpful comments on the manuscript. \added{Data collection and sharing for this project was provided by the Cambridge Centre for Ageing and Neuroscience (CamCAN). CamCAN funding was provided by the UK Biotechnology and Biological Sciences Research Council (grant number BB/H008217/1), together with support from the UK Medical Research Council and University of Cambridge, UK. This manuscript was prepared using a limited access dataset obtained from the Child Mind Institute Biobank, The Healthy Brain Network dataset. This manuscript reflects the views of the authors and does not necessarily reflect the opinions or views of the Child Mind Institute}
